SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-31 docs/questioning.tex
new CSRF defences
updated the availability table

Table~\ref{tab:avail} presents
our findings regarding the availability of the mechanism
in terms of source code and corresponding executables.
We also examined the availability of the testbeds mentioned in the paper.
The check mark (\tick) indicates that at some point within the publication,
there is a homepage where the reader can refer to, to download the
corresponding software. {\sc ao} (Available On-line) suggests that
the software is available on-line but the address was not mentioned
in the paper, which probably indicates that the authors made
it available after the publication. The question mark ({\bf ?}),
indicates that the a homepage for the software was included
in the publication but now it is not available.

@@

\noindent
{\sc soma}~\cite{OWVS08} is a policy enforcement framework that
can actually detect such an attack (along with some architectures
presented in Subsubsection~~\ref{sec:mashups}).
To achieve this, {\sc soma} requires site administrators
to specify legitimate, external domains for sending
or receiving information in order to approve interactions
between them and the protected web site.

@@

  \multirow{9}{*}{Policy Enforcement}

@@

@@

  &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% & {\sc xss}, {\sc csrf}\\

@@

@@

	\multirow{9}{*}{Runtime Tainting}
	% &  	{\it SecuriFly}~\cite{MLL05}  & - & - & - \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & {\sc ao} & {\sc na} & {\sc ao} \\

@@

  &   {\it {\sc sqlg}uard}~\cite{BWS05} & {\sc ao} & {\sc ao} & {\sc na} \\

@@

  \multirow{4}{*}{Code Rewriting}
  &   {\it CoreScript}~\cite{YCIS07} & {\sc ao} & {\sc na} & {\sc na} \\
  \multirow{5}{*}{Securing Mashups}
  &   {\it ConScript}~\cite{ML10} & {\sc ao} & {\sc na} & {\sc na} \\
  &   {\it TreeHouse}~\cite{IW12} & {\sc na} & {\sc na} & {\sc na} \\
	\multirow{7}{*}{Policy Enforcement}
	&   {\it {\sc met}}~\cite{ELX07} & {\sc na} & {\sc na} & {\sc na} \\
        \multirow{7}{*}{Training}

@@

	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & {\sc na} & {\sc ao} & {\sc na} \\

@@

	% & 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & {\bf ?} & {\bf ?} & {\bf ?} \\

@@

       download the corresponding software. {\sc ao} (Available On-line) suggests

>>>>

Table~\ref{tab:avail} presents
our findings regarding the availability of the mechanism
in terms of source code and corresponding executables.
We also examined the availability of the testbeds mentioned in the paper.
The check mark (\tick) indicates that at some point within the publication,
there is a homepage where the reader can refer to, to download the
corresponding software. {\bf AO} (Available On-line) suggests that
the software is available on-line but the address was not mentioned
in the paper, which probably indicates that the authors made
it available after the publication. The question mark ({\bf ?}),
indicates that the a homepage for the software was included
in the publication but now it is not available.

@@

\noindent
{\sc soma}~\cite{OWVS08} is a policy enforcement framework that
can actually detect such an attack (along with some architectures
presented in Subsubsection~~\ref{sec:mashups}).
To achieve this, {\sc soma} requires site administrators
to specify legitimate, external domains for sending
or receiving information in order to approve interactions
between them and the protected web site. As a result,
{\sc soma} can also detect {\sc csrf} attacks.

@@

  \multirow{12}{*}{Policy Enforcement}

@@

  &   {\it NoForge}~\cite{JKK06a} & 35 & (7,{\sc nq},{\sc nq},0)\_r & {\bf ?} & {\sc csrf} \\

@@

  &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% & {\sc xss}, {\sc csrf} \\
  &   {\it Barth et al.}~\cite{BJM08} & 271 & & {\bf ?} & {\sc csrf} \\

@@

  &   {\it CsFire}~\cite{DDHPJ10} & & & {\bf ?} & {\sc csrf} \\

@@

  &   {\it {\sc sqlg}uard}~\cite{BWS05} & {\bf AO} & {\bf AO} & {\sc na} \\
  \multirow{12}{*}{Policy Enforcement}
  &   {\it NoForge}~\cite{JKK06a} & {\bf AO} & {\bf AO} & {\sc na} \\
  % &   {\it {\sc met}}~\cite{ELX07} & {\sc na} & {\sc na} & {\sc na} \\
  &   {\it CoreScript}~\cite{YCIS07} & {\bf AO} & {\sc na} & {\sc na} \\
  &   {\it Barth et al.}~\cite{BJM08} & {\sc na} & {\sc na} & {\sc na} \\
  &   {\it ConScript}~\cite{ML10} & {\bf AO} & {\sc na} & {\sc na} \\
  &   {\it CsFire}~\cite{DDHPJ10} & \tick & {\sc na} & {\sc na} \\
  % &   {\it TreeHouse}~\cite{IW12} & {\sc na} & {\sc na} & {\sc na} \\

@@

	&  	{\it {\sc php} Aspis}~\cite{PMP11} & {\bf AO} & {\sc na} & {\bf AO} \\

@@

@@

	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & {\sc na} & {\bf AO} & {\sc na} \\

@@

@@

       download the corresponding software. {\bf AO} (Available On-line) suggests
